Parsing Postfix log files

### 2009-02-16 doc/logparser-background.tex
Remainder of the corrections to the background chapter.

    \item Sender Policy Framework (SPF)~\cite{openspf}.  SPF\label{spf
        introduction} records specify which mail servers are allowed to
        send mail claiming to be from a particular domain.  The intention
        is to reduce spam from faked sender addresses,
        backscatter~\cite{postfix-backscatter}, and
        joe~jobs~\cite{Wikipedia-joe-job}\glsadd{Joe job}.  There has been
        considerable resistance to the proposal because it breaks or vastly
        complicates some features of \acronym{SMTP}, e.g.\ forwarding mail
        from one company or university to another when a user moves.

    \item Greylisting~\cite{greylisting} is a technique that temporarily
        rejects a delivery attempt when the triple of \newline{}
        \tab{}\texttt{(sender address, recipient address, remote
        \acronym{IP} address)}\newline{} has not been seen before; on
        second and subsequent delivery attempts from that triple the mail
        will be accepted.  This blocks spam because maintaining a list of
        failed addresses and retrying after a temporary failure is
        uneconomical for a spam sender, but a legitimate mail server must
        retry deliveries that temporarily failed.  Sadly spam senders are
        using increasingly complex and well written programs to distribute
        spam, frequently using an ISP provided \acronym{SMTP} server from a
        compromised machine on the ISP's network.  Greylisting will slowly
        become less useful, but it does block a large percentage of spam
        mail at the moment; the most effective restrictions from the
        \numberOFlogFILES{} log files used in testing the parser are shown
        in \tableref{Summary of rejections}.  Greylisting is obviously
        worth using, at least at the moment, particularly when you take
        into account Greylisting's position as the final restriction that a
        mail must overcome:\footnote{Greylisting is the final restriction a
        mail must overcome in the configuration used on the mail server the
        log files were obtained from; an administrator is free to use
        Greylisting wherever in the restriction list they feel is most
        appropriate for their mail system.} Greylisting only takes effect
        for mails that have passed every other restriction.  Some problems
        may be encountered when using greylisting: some servers fail to
        retry; legitimate mail may be delayed, particularly when coming
        from a pool of servers.

@@

    \item Scoring systems such as Policyd-weight~\cite{policyd-weight}
        perform tests on features of the delivery attempt (e.g.\
        \acronym{IP} address, sender address), incrementing or decrementing
        a score based on the results; if the eventual score is higher than
        a threshold the mail is rejected.  The administrator must manually
        whitelist clients if they are to bypass a Postfix restriction;
        using a threshold that requires a delivery attempt to hit several
        restrictions frees the administrator from whitelisting clients that
        fall foul of one restriction only.

    \item Rate limiting on a per-sender, per-client or per-recipient basis
        as performed by Policyd~\cite{policyd}.

@@

This section has provided background information on several topics,
starting with the motivation behind the project, continuing with an
explanation of the use of a database as an \acronym{API} and an
introduction to \acronym{SMTP}.  The focus then switched to Postfix, the
\acronym{MTA} in use, and its restrictions and policy servers.

>>>>

    \item Sender Policy Framework (SPF)~\cite{openspf}.  SPF\label{spf
        introduction} records specify which mail servers are allowed to
        send mail claiming to be from a particular domain.  The intention
        is to reduce spam from faked sender addresses,
        backscatter~\cite{postfix-backscatter}, and
        joe~jobs~\cite{Wikipedia-joe-job}\glsadd{Joe job}.  There has been
        considerable resistance to the proposal because it breaks or vastly
        complicates some features of \acronym{SMTP}, e.g.\ forwarding mail
        from one domain to another when a user moves.

    \item Greylisting~\cite{greylisting} is a technique that temporarily
        rejects a delivery attempt when the triple of \newline{}
        \tab{}\texttt{(sender address, recipient address, remote
        \acronym{IP} address)}\newline{} has not been seen before; on
        second and subsequent delivery attempts from that triple the mail
        will be accepted.  This blocks spam from some senders because
        maintaining a list of failed addresses and retrying after a
        temporary failure is uneconomical for a spam sender, but a
        legitimate mail server must retry deliveries that failed
        temporarily.  Sadly spam senders are using increasingly complex and
        well written programs to distribute spam, frequently using an ISP
        provided \acronym{SMTP} server from a compromised machine on the
        ISP's network.  Greylisting will slowly become less useful, but it
        does block a large percentage of spam mail at the moment; the most
        effective restrictions from the \numberOFlogFILES{} log files used
        when generating the results in \sectionref{Results} are shown in
        \tableref{Summary of rejections}.  The table shows that greylisting
        is worth using at the moment, particularly when you take into
        account its position as the final restriction that a mail must
        overcome in the configuration used on the mail server that
        generated the log files: on that server greylisting only takes
        effect for mails that have passed all other restrictions.  Some
        problems may be encountered when using greylisting: some servers
        fail to retry after a temporary failure, or legitimate mail may be
        delayed, particularly when coming from a pool of servers.

@@

    \item Scoring systems such as Policyd-weight~\cite{policyd-weight}
        perform tests on features of the delivery attempt (e.g.\
        \acronym{IP} address, sender address), incrementing or decrementing
        a score based on the results; if the eventual score is higher than
        a threshold the mail is rejected.  The administrator must manually
        whitelist clients if they are to bypass a Postfix restriction,
        whereas using a threshold that requires a delivery attempt to hit
        several scored restrictions frees the administrator from
        whitelisting clients that fall foul of one binary restriction only.

@@

This section has provided background information useful in understanding
this thesis, starting with the motivation behind the project, continuing
with an introduction to \acronym{SMTP}, and finishing with Postfix, its
anti-spam restrictions, and its support for policy servers.

### 2009-02-16 doc/logparser.tex
Dealt with some XXX items.
Fixed acronyms so they work properly, get expanded when appropriate, and add the     correct entries to the glossary and acronym appendices. Correct capitalisation of most section and subsection headings. Corrections made to background chapter; more remain to be made.
Fixed some 'overfull hbox' problems.
Remainder of the corrections to the background chapter.

% Acronyms and glossary entries.  Useful options:
% * nonumberlist disables the list of page numbers after each entry.
\usepackage[acronym,toc,numberedsection=autolabel,style=list,nonumberlist]{glossaries}
\renewcommand{\glspostdescription}[0]{}
\renewcommand{\glsautoprefix}[1]{glossary:#1}
\newglossary[plg]{postfix}{pin}{pout}{Postfix Daemons}
\makeglossaries{}

@@

\newcommand{\tab}[0]{%
    \hspace*{2em}%
}

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\gls{PLP}}
\newcommand{\parsernames}{\gls{PLP}'s}

@@

XXX GENERATE RESULT\_COLS AND CONNECTION\_COLS AUTOMATICALLY\@.

@@

XXX IMPROVE BIBLIOGRAPHY APPEARANCE\@: NAMES LOOK UGLY (E.G.\ P.\
\empty{}.\ Porters)\@.

>>>>

% Acronyms and glossary entries.  Useful options:
% * nonumberlist disables the list of page numbers after each entry.
\usepackage[acronym,toc,numberedsection=autolabel,style=list,nonumberlist]{glossaries}
\renewcommand{\glspostdescription}[0]{}
\renewcommand{\glsautoprefix}[1]{glossary:#1}
\newglossary[plg]{postfix}{pin}{pout}{Postfix Daemons}
\makeglossaries{}
\newcommand{\acronym}[1]{%
    \gls{#1}\glsadd{#1 glossary}%
}

@@

\newcommand{\tab}[0]{%
    \hspace*{1em}%
}

@@

% The name of the program, so I only have to change it in one place.
\newcommand{\parsername}{\acronym{PLP}}
\newcommand{\parsernames}{\acronym{PLP}'s}

@@

@@

XXX CHECK URLS FOR BIBLIOGRAPHY ENTRIES, AND UPDATE LAST CHECKED DATES\@.

XXX SHOULD I SCRAP postfix\_action?

XXX ANNOTATE ALL URLS WITH LAST CHECKED DATE\@.

XXX STANDARDISE ON ``email'' OR ``mail'' EVERYWHERE\@?

xXX IMPROVE BIBLIOGRAPHY APPEARANCE\@: NAMES LOOK UGLY (E.G.\ P.\
\empty{}.\ Porters)\@.

XXX CHECK WITH CARL ABOUT CAPITALISATION IN SECTION AND SUBSECTION
HEADINGS\@.
